R Notebook

### 2022-04-12 R/DeaminationAnalysis.rmd
Update DeaminationAnalysis.rmd

```{r periodicity_stats}
print(mutperiodData$periodicityResults)
```

@@

>>>>

@@

```{r acquire_and_format_data_3}
load(file.path(deaminationDataDirectory, "TCG_deamination_periodicity_results.rda"))
dataSetNames = as.list(setNames(nm = mutperiodData$periodicityResults$Data_Set))

```{r TCG_CPD_rotational_periodicity_trinuc_normalized}
parseAndPlotPeriodicity(
  dataSetNames$TCG_NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
  title = "TCG CPD 1hr Rep1 Rotational Trinuc Norm")
parseAndPlotPeriodicity(
  dataSetNames$TCG_NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
  title = "TCG CPD 24hr Rep1 Rotational Trinuc Norm")
parseAndPlotPeriodicity(
  dataSetNames$TCG_NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
  title = "TCG CPD 48hr Rep1 Rotational Trinuc Norm")
```

```{r TCG_CPD_rotational_periodicity_XR-seq_normalized}
parseAndPlotPeriodicity(
  dataSetNames$TCG_NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
  title = "TCG CPD 1hr Rep1 Rotational XR-seq Norm")
parseAndPlotPeriodicity(
  dataSetNames$TCG_NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
  title = "TCG CPD 24hr Rep1 Rotational XR-seq Norm")
parseAndPlotPeriodicity(
  dataSetNames$TCG_NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
  title = "TCG CPD 48hr Rep1 Rotational XR-seq Norm")
```

```{r TCG_CPD_translational_periodicity_trinuc_normalized}
parseAndPlotPeriodicity(
  dataSetNames$`TCG_NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
  title = "TCG CPD 1hr Rep1 Rotational Trinuc Norm")
parseAndPlotPeriodicity(
  dataSetNames$`TCG_NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
  title = "TCG CPD 24hr Rep1 Rotational Trinuc Norm")
parseAndPlotPeriodicity(
  dataSetNames$`TCG_NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
  title = "TCG CPD 48hr Rep1 Rotational Trinuc Norm")
```

```{r TCG_CPD_translational_periodicity_XR-seq_normalized}
parseAndPlotPeriodicity(
  dataSetNames$`TCG_NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
  title = "TCG_CPD 1hr Rep1 Rotational XR-seq Norm")
parseAndPlotPeriodicity(
  dataSetNames$`TCG_NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
  title = "TCG CPD 24hr Rep1 Rotational XR-seq Norm")
parseAndPlotPeriodicity(
  dataSetNames$`TCG_NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
  title = "TCG CPD 48hr Rep1 Rotational XR-seq Norm")
```
